GEE models

### 2017-07-05 doc/manuscript.Rmd
updated inline results funs and updated basic char results

```{r inline_results}
pct_nefa <- calc_pct_nefa(project_data)
chg_outcomes <- calc_outcomes_chg_n(project_data)
dm_incid <- calc_conversion_dysgly('ConvertDM')
predm_incid <- calc_conversion_dysgly('ConvertPreDM')

ds0yr <- dplyr::filter(project_data, VN == 0)
female <- calc_npercent(ds0yr$Sex, 'Female')
european <- calc_npercent(ds0yr$Ethnicity, 'European')
famhist <- calc_npercent(ds0yr$FamHistDiab, 'Yes')
est_gee <- calculate_gee_magnitude(gee_results)
```

@@

For this study, there were 
`r sex.npct$npct` females and `r ethn.npct$npct` had European-ancestry.
The average age of the participants was `r aide::average(ds0yr$Age)` years 
(`r aide::stddev(ds0yr$Age)` SD) and the average BMI was
`r aide::average(ds0yr$BMI)` (`r aide::stddev(ds0yr$BMI)` SD). Most of the 
participants, `r fhd.npct$npct`, had a family history of diabetes.
Insulin sensitivity and beta-cell function measures showed a significant median
decline between
`r percent.change.outcomes$chg` (p`r percent.change.outcomes$p`) over the 6
years in this analysis of the PROMISE cohort.
Consistent with this decline, there were `r dm.convert`
participants who developed diabetes while `r predm.convert` participants either
converted to or maintained IFG or IGT status over the 6 years.
<!-- maintain vs convert -->

`r cite_f('nefaDist')` shows the compositional distribution of NEFA in the study
participants. Four individual NEFA made up the vast majority 
(`r sum(percent.nefa$pct)`%) of the total NEFA fraction. The largest contributors
were `r percent.nefa$c[1]`, `r percent.nefa$c[2]`, `r percent.nefa$c[3]`, and 
`r percent.nefa$c[4]`. Raw concentration values are shown in `r cite_st('nefaDist')`. 
All individual NEFA as well as the total fraction had
correlations that ranged from weak to null (r<0.3) with participant
characteristics (see `r cite_sf('corr')`).

>>>>

```{r inline_results}
nefa <- calc_pct_nefa(project_data)
chg_outcomes <- calc_outcomes_chg_n(project_data)

ds0yr <- dplyr::filter(project_data, VN == 0)
female <- calc_npercent(ds0yr$Sex, 'Female')
european <- calc_npercent(ds0yr$Ethnicity, 'European')
famhist <- calc_npercent(ds0yr$FamHistDiab, 'Yes')
est_gee <- gee_results %>% 
    dplyr::filter(model == "Adjusted") %>% 
    calc_gee_magnitude()
```

@@

For this study, there were 
`r female$npct` females and `r european$npct` had European-ancestry (see 
`r cite_t("basic")`). The mean follow-up time was `r calc_followup_time()`
years, where `r calc_pct_full_visits()`% of participants attended all three
visits.
The average age of the participants was `r aide::average(ds0yr$Age)` years 
(`r aide::stddev(ds0yr$Age)` SD) and the average BMI was
`r aide::average(ds0yr$BMI)` (`r aide::stddev(ds0yr$BMI)` SD). Most of the 
participants, `r famhist$npct`, had a family history of diabetes.
Insulin sensitivity and beta-cell function measures showed a significant median
decline between
`r pct_outcomes$chg` (p`r pct_outcomes$p`) over the 6
years in this analysis of the PROMISE cohort.
Consistent with this decline, there were `r calc_incid_dysgly("ConvertDM")`
and `r calc_incid_dysgly("ConvertPreDM")`incident cases of diabetes and pre-diabetes (IFG and IGT),
respectively, over the 6-years. Incident diabetes cases were excluded from further GEE
analyses.

`r cite_f('nefa')` shows the compositional distribution of NEFA in the study
participants. Four individual NEFA made up the vast majority 
(`r sum(nefa$pct)`%) of the total NEFA fraction. The largest contributors
were `r nefa$c[1]`, `r nefa$c[2]`, `r nefa$c[3]`, and 
`r nefa$c[4]`. Raw concentration values are shown in `r cite_st('nefa')`. 
There were no differences in individual NEFA for those who did compared to those
who did not take medications to manage blood lipids (data not shown).
All individual NEFA as well as the total fraction had
correlations that ranged from weak to null (r<0.3) with participant
characteristics (see `r cite_sf('corr_conc')` and `r cite_sf("corr_pct")`).
